### 2017-03-20 Writing/TrafficAnalysisOn6LoWPAN/device.tex
A New Hope

\section{Distinguish Hardware}\label{Sec:DistinguishDevice}
%Basic idea of this attack
IoT applications utilise a great variation of devices, with each having different processing power. Consequently, the time required for a specific operation could be exploited as an indicator to the hardware.

The time required to process a PING Request could therefore be exploited to perform such hardware distinguishing attack. Although the same attack could be conducted on various packets, PING is specifically practical and ideal due to:
\begin{enumerate}
	\item PING is processed in a highly predictable manner where nearly no computation is required; thus minimises the noise induced by data dependency.
	\item Support to PING is mandatory according to the standard\cite{rfc4443}, making the attack universally applicable.
\end{enumerate}

For our experiments, the PING Requests are initiated from a Linux machine connected into the 6LoWPAN through a border router. The ``-s 0'' option is specified for the `ping6' command in order to avoid exceeding the MTU of 6LoWPAN (127 bytes).

\subsection{Computing PING Response Time}\label{TimingWithContikiMAC}
%How to process the packets
%ContikiMAC
For energy preservation, Contiki adopts a Radio Duty Cycle (RDC) protocol called Contiki MAC\cite{ContikiMAC}. On receiver's side, Contiki MAC switches off the radio for most of the times and periodically wakes up for a short period for signal detection. If a signal is detected during the awaken period, the radio is kept on to receive a packet, followed by an acknowledgement sent to inform the sender. On sender's side, a packet is repeatedly transmitted until timed out or an acknowledgement is received.

Therefore when ContikiMAC is enabled by default, duplicated packets may be observed in the captured traffic. As an approximation to the PING Request processing time, we define PING Response Interval (PRI) as the time elapsed between the last PING Request and the first PING Response.

\begin{example}
%\paragraph{Example}

\AddFigure{fig/PRI.png}{PRI Example}{PRIExample}

\Cref{PRIExample} shows an example of packets captured by Wireshark\cite{Wireshark}. Duplicated PING Requests, No.$198$ to No.$203$, are replied by a single PING Response, No.$205$, matched by their \textit{seq} field ($16$). The PRI is therefore computed as the difference in time between No.$203$ (last PING Request) and No.$205$ (first PING Response) which is:
\begin{equation*}
PRI = 4.701468 - 4.684369 = 0.017099(s) = 17.099(ms)
\end{equation*}
\end{example}

\subsection{PRIs of TelosB and CC2538} \label{PRI_Devices}

\Cref{PRIs} shows the distributions of PRI collected on TelosB and CC2538. The bar on the right most represents the outliers in the data, with $9.43\%$ on TelosB are $\geq 19$ms and $2.60\%$ on CC2538 $\geq 12$ms respectively.

The result of \Cref{PRIs} suggests that TelosB and CC2538 can be easily distinguished by their PRIs, as they are tightly clustered around $17$ms for TelosB and $9.5$ms for CC2538 respectively.

\begin{figure}[ht!]
	\centering
	\begin{subfigure}{0.45\linewidth}
		\includegraphics[width=\linewidth]{fig/helloworld_sky.png}
		\subcaption{TelosB PRIs}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\includegraphics[width=\linewidth]{fig/helloworld_cc2538.png}
		\subcaption{CC2538 PRIs}
	\end{subfigure}

	\adjustbox{max width = \textwidth}
	{
		\begin{tabular}{|c|c|c|}
			\hline
			              & Mean (ms)     & Median (ms)   \\ \hline
			TelosB  & 33.82 & 17.03 \\ \hline
			CC2538 & 14.27         & 9.56          \\ \hline
		\end{tabular}
	}
	\caption{PRIs for different devices. \label{PRIs}}
\end{figure}

With respect to the outliers, one common cause is the processor being occupied by other tasks when a PING Request is received; thus delayed the processing of PING as illustrated by \Cref{PingProbeExample}. The portion of the outlier is hence affected by the payload on the node and the frequency of PING requests. We discuss further details of the outliers in \Cref{PingProbe}.

\AddFigure{fig/PingProbe_Session.png}{PRI prolonged by Sensor Reading}{PingProbeExample}

\subsection{Factors Affecting PRI} \label{PingDevice}

Despite the clear distinguishability suggested by \Cref{PRI_Devices}, there exists several practical factors the might affect the result.

802.15.4 Security\cite{802154} is a prominent factor to PRIs as it induces several cryptographic operations which are computationally heavy and hence could significantly increase the PRI. \Cref{802154SecPRI} illustrates the PRIs on the same devices when 802.15.4 Security is enabled. Flooding PING could also make an impact on measuring PRIs as it will overrun the low processing power of these resource constrained devices.

\begin{figure}[ht!]
	\centering
	\begin{subfigure}{0.4\textwidth}
	{
		\includegraphics[width=\textwidth]{fig/noncoresec_ping_telosb_sw.png}
	}
	\end{subfigure}
	\begin{subfigure}{0.4\textwidth}
	{
		\includegraphics[width=\textwidth]{fig/noncoresec_ping_telosb_hw.png}
	}
	\end{subfigure}
	\begin{subfigure}{0.4\textwidth}
	{
		\includegraphics[width=\textwidth]{fig/noncoresec_ping_cc2538_sw.png}
	}
	\end{subfigure}

	\adjustbox{max width = \textwidth}
	{
		\begin{tabular}{|c|c|c|}
			\hline
			              & Mean (ms)     & Median (ms)   \\ \hline
			TelosB HW AES & 37.20 & 30.77 \\ \hline
			TelosB SW AES & 105.19        & 87.40          \\ \hline
			CC2538 SW AES & 48.83         & 24.55          \\ \hline
		\end{tabular}
	}

	\caption{PRIs with 802.15.4 security\label{802154SecPRI}}
\end{figure}

>>>>

\section{Leakage on Device Information}

Different processors result into different response time to the same message; hence the response time can be correlated to the MCU.

\begin{itemize}
	\item PING is a ideal feature in ICMP to launch this attack.
\end{itemize}

The processor can be considered a hint for the adversary to find out the model of target device.

### 2017-03-20 Writing/TrafficAnalysisOn6LoWPAN/introduction.tex
A New Hope

\section{Introduction}
Traffic Analysis is a well studied technique that breaches data confidentiality over Internet which exploits the side channel information, such as packet length and timing, to reveal contents in the encrypted traffic. As a matter of fact, Traffic Analysis techniques is often associated with malicious Internet behaviour such as privacy violation and mass surveillance.

%typically targeting protocols including HTTPS\cite{rfc2818} and SSL\cite{rfc6101}/TLS\cite{rfc5246}. This type of attacks works by correlating the encrypted contents to side channel information frequently omitted by cryptographic scheme designs, such as packet length, timing and any other unprotected meta data. Consequently, TA is often associated to Internet privacy violation and Mass Surveillance.

On the other hand, the development of Internet of Things (IoT) has linked ever more private data to the network, with radio being the most extensively used media for data transmission. These factors combined made Traffic Analysis posing even greater threat in the IoT context, as data are made widely open yet its content are juicier than ever.

%The extensive use of radio communication in exposed environment poses a great security challenge to IoT applications, especially against TA attacks as packets containing critical privacy data, e.g. driving information in Vehicular Ad Hoc Networks(VANETs)\cite{VANET} and daily life data in a smart house, can be easily eavesdropped and analysed by adversaries.

In this paper, we revised the applicability of Traffic Analysis in IoT applications by demonstrating simple examples capturing the concept. We made extensive use of Contiki OS\cite{Contiki} in our experiments to build demo applications. A 6LoWPAN\cite{rfc4944} network is built on two models of typical devices, namely TelosB\cite{TelosB} and CC2538\cite{CC2538}, as well as a network constructed by simulated Wismote\cite{Wismote}.

%Finally the paper structure
The paper is structured as follows. We first review the related literatures in \Cref{RelatedWork} and briefly report a security flaw in Contiki source code in \Cref{noncoresec}. We then present the first example that extracts ICMP\footnote{Specifically, the term ICMP we used in this paper refers to ICMPv6.}\cite{rfc4443} messages in \Cref{ICMPAttack}, followed by another example that reveals hardware information in \Cref{Sec:DistinguishDevice}. \Cref{PingProbe} proposes a new type of side channel attack, we named PingProbe, that fingerprints the application running on an IoT node. Finally we conclude the paper in \Cref{conclusion}.

\section{Related Work \label{RelatedWork}}
%Literatures about Traffic Analysis...
Traffic Analysis is a well studied subject in the Internet security and privacy community. \cite{WebSidechannel} summarised several scenario of side channel attacks against web applications, followed by \cite{PinpointWeb} which proposes the use of Mutual Information to pinpoint the potential points of information leakage. \cite{AppleMsg}, \cite{Language} and \cite{VideoTraffic} described attacks against encrypted text, voice and video traffic respectively, while \cite{SuggestBox} instantiated an attack against Google search box. \cite{HClassifier} and \cite{Peekaboo} studied different classifiers when adopting Machine Learning in Traffic Analysis. Different countermeasures are studied by \cite{TrafficMorphing}, \cite{HTTPOS} and \cite{FTE}.

%Literatures about 6LoWPAN security
With respect to 6LoWPAN security issues, \cite{6LoWPANAtk} summarises the known attacks in 6LoWPAN networks, including Fragmentation Attack\cite{FragAtk}, Sinkhole Attack\cite{Sinkhole}, Hello Flood Attack\cite{HelloFlood}, Wormhole Attack\cite{Wormhole} and Blackhole Attack\cite{Blackhole}. In addition, \cite{802154SecIssues} reported certain problematic designs in 802.15.4 security\cite{802154}.

%To our knowledge, this is the first proposal of such type of our fingerprint attack in \Cref{PingProbe}.

>>>>

\section{Introduction}
\begin{itemize}
	\item Motivation
	\item Related Work
\end{itemize}
